The Effect of Void on the Cold Deformation Behaviour of $\alpha_2+\gamma$ Two Phase Ti-Al Alloy

### 2018-10-09 draft/alexpub.tex
midified

Defects such as grain boundary, void and segregation plays an significant role in the process of fracture \cite{Larsen2016}. In order to understanding the mechanism of brittle fracture, multi-scale methods from micro to marco scale have been applied to investigate the behavior of fracture. It's necessary to carefully examine the revolution of defects and its influence on the fracture process at atomic scale. A previous study on void growth in gamma-TiAl single crystal has reveals that void with high volume fraction detracts incipient yield strength \cite{Tang2014}.Molecular dynamics(MD method has been use to investigate the evolution of void in materials in nanoscale \cite{Jing2018a,Elkhateeb2018,Tang2014}. The fracture mechanisms in the duplex micro-structure are plasticity induced grain boundary decohesion and cleavage, while those in the lamellar micro-structure are interface delamination and cracking across the lamellar \cite{}.

@@

The interaction of particle in the material is determined by interatomic potential. Many reported examples of crack propagation in metal materials were performed with embedded atomic method due to is better accuracy in metal lattice compare with F-S and L/J \cite{Goes1998}. The embedded atom method (MEAM) potential developed by Zope and Mishin \cite{Zope2003} was used in the study. The simulation is submitted by MD simulations with the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code \cite{Plimpton1995}. We performed constant-pressure and constant-temperature (NPT) molecular dynamics simulation.

@@

where $E_{total}$ is the total energy of the system, $\rho_{h,i}$, is the host electron density at atom $i$ due to the remaining atoms of the system,$F_i(\rho)$ is the energy for embedding atom i into the background electron density $\rho$, and $\phi_{ij}(R_{ij})$ is the core-core pair repulsion between atoms $i$ and $j$ separated by the distance $R_{ij}$. It can be noted that $F_i$ only depends on the element of atom $i$ and $\phi_{ij}$ only depends on the elements of atoms $i$ and $j$. The electron density is, as stated above, approximated by the superposition of atomic densities.

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=1\linewidth]{img/models}
	\caption{Overview of model creation}
	\label{fig:model-creation}
\end{figure}
\cite{}
$\gamma $ TiAl has a fcc-centered tetragonal with an $L1_0$ structure \cite{}, and $\alpha_2 TiAl$ is hcp structure, the structure of the two initial cells are shown in Fig.\cite{}, and the constructing parameters are givin by Table.\cite{}. The simulation cells of two phase polycrystalline with an initially spherical void at different position are shown in figure \cite{}. Periodic boundary conditions (PBC)are applied along all three directions, that makes poly crystal with periodic nanovoid structures. The initial dimension of simulation cell is  $L_x = $ nm, $L_y = $ nm, $L_z = $ nm, and each model contains about 4.6 million atoms. The grain orientation and size were randomly created with Voronoi method with code ATOMSK \cite{}, and resulting in the arbitrary shape and orientation of the grains. Only one spherical void defect was placed intragranularlly or intergranularlly within each simulation model void within each simulation model. The intragranular spherical void was located in grain interior of the largest grain of the simulation model, as shown in Fig. \cite{}. The intergranular spherical void was at the center of the simulation cell, as shown in Fig. \cite{}.

@@

	% \begin{figure}[ht]
	% 	\centering  
	% 	\includegraphics[width=0.7\linewidth]{img/cell}
	% 	\caption{unit cell}
	% 	\label{fig:unit_cell}
	% \end{figure}

@@

\subsection{Deformation Behaviour of Two Phase Alloys without Void Defects}
However, the following discussion concentrates on deformation phenomena that rely on the elastoplastic codeformation of the $\gamma$ and $\gamma_2$ phases and on the particular point defect situation occurring in twophase alloys. Due to this effect ( $\alpha_2$ + $\gamma$ ) alloys exhibit some remarkable properties that are unlike those of either constituent.
\begin{figure}[ht]
		\centering
		\includegraphics[width=1\linewidth]{img/def-gamma}
		\label{fig:def-gamma}
		\caption{$\gamma$ phase deformation}
\end{figure}
The configure of atoms is shown in Fig.\ref{fig:yield}, it can be seen that dislication emission initiate in $\gamma$ pahse in XXX ps, and the deformation canbe mainly confied to the majority $\gamma$ pahse. $\gamma$(TiAl) deforms by octahedral glide of ordinary dislocations with the Burgers vector b=1/2<110] and superdislocations with the Burgers vectors b=<101] and $b=1/2<11\overline{2}]$. The other potential deformation mode is mechanical twinning along $1/6<11\overline{2}]{111}$.
From Fig.\ref{fig:yield}, of the two constituents of ($\alpha_2$+$\gamma$) alloys, the $\alpha_2$ phase is more difficult to deform. A reason for the unequal strain partitioning between the $\alpha_2$ and $\gamma$ phase is certainly the strong plastic anisotropy of the $\alpha_2$ phase. TEM examinations performed on tensile  tested lamellar alloys have revealed that the limited plasticity of the $\alpha_2$ phase is mainly carried by local slip of <a>-type dislocations with the Burgers vector $b=1/3<11\overline{2}0>$ prism planes\ref{fig:yield}, which is by far the easiest slip system in $\alpha_2$ single crystals. 
	\begin{figure}[ht]
		\centering
		\includegraphics[width=1\linewidth]{img/def-alpha}
		\label{fig:def-alpha_2}
		\caption{$\alpha_2$ phase deformation}
	\end{figure}
Basic deformationg mechanism of $\alpha_2$ phase

@@

%	\begin{figure}[ht]
%		\centering
%		\includegraphics[width=1\linewidth]{img/disl2-gamma}
%		\label{fig:surf}
%		\caption{stress-strain curve}
%	\end{figure}
1.In many cases the orientation of slip slip is changed because the crystallographically available slip and directions are not continuous across the interface. This may significantly reduce the Schmid factor and thus impede slip transfer. At the $\gamma/\gamma$ interfaces the orientation of the slip plan could change through a relevantly large angle of about 90 degree. Reorientation of slip is always required at the $\alpha_{2}/\gamma$ interface; the smallest angle between the corresponding slip planes ${1 1 1 }_{\gamma}$ and ${ 1 0 -1 0}_{\alpha_2}$ is about 19 degree \cite{}.

The core of  a dislocation intersecting an interface often needs to be transformed. For example, an ordinary 1/2<110] dislocation gliding in one $\gamma$ grain has to be converted in to a <101] super dislocation with the double Burgers vector gliding in an adjacent $\gamma$ grain. At the $\alpha_2/\gamma$ interface the dislocations existing in the $D0_{19}$ structure have to be transformed into dislocations consistent with the $L1_0$structure. These core transformations are associated with a change of the dislocation line energy because the lengths of the Burgers vectors and the shear module are different.

@@

	%\subsection{Fracture Process with Integranular Void }

	%\subsection{Fracture Process with Intergranular Void }

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=1\linewidth]{"img/dis-void"}
	\caption{Atoms configuration around void ($\alpha$ phase atoms have been removed)}
	\label{fig:dis-void}
\end{figure}

\begin{figure}[ht]
	\centering
	\includegraphics[width=1\linewidth]{"img/orowan"}
	\caption{Schematic of Orowan process}
	\label{fig:dis-void}
\end{figure}

@@

	%\begin{figure}[ht]
	%	\centeringT
	%	\includegraphics[width=0.7\linewidth]{img/allline}
	%	\caption{Fracture process of specimen with void in $\alpha_2$ phase}
	%	\label{ }
	%\end{figure}
	%

@@

According to Schmid's law:
	$$\tau = \sigma*m$$
where m is the Schmid factor :
	$$ m = cos(\phi)cos(\lambda)$$
	%\subsection{The influence of void on strength of TiAl alloy}
%	\begin{figure}[ht]
%		\centering
%		\includegraphics[width=0.7\linewidth]{img/frame2}
%		\caption{stress-$\sigma$=0}
%		\label{ }
%	\end{figure}
%	
%	\begin{figure}[ht]
%		\centering
%		\includegraphics[width=0.7\linewidth]{img/frame150}
%		\caption{stress-$\sigma$=0.15}
%		\label{ }
%	\end{figure}
%	
%	\begin{figure}[ht]
%		\centering
%		\includegraphics[width=0.7\linewidth]{img/frame160}
%		\caption{stress-$\sigma$=0.16}
%		\label{ }
%	\end{figure}
%	
%	\begin{figure}[ht]
%		\centering
%		\includegraphics[width=0.7\linewidth]{img/frame170}
%		\caption{stress-$\sigma$=0.17}
%		\label{ }
%	\end{figure}
%	
%	
%	\begin{figure}[ht]
%		\centering
%		\includegraphics[width=0.7\linewidth]{img/frame180}
%		\caption{stress-$\sigma$=0.18}
%		\label{ }
%	\end{figure}
%The location of void affects strength of material. Comparing with the model with integranular void, the model with %intergranular voids is weaker. atomic stress is calculated 
%	
%	
%	
%	
%	
%	% \begin{figure}[ht]
%	% 	\centering
%	% 	\includegraphics[width=0.7\linewidth]{img/ialine}
%	% 	\caption{stress-strain curve}
%	% 	\label{fig:ia_line}
%	% \end{figure}
%	% 
%	% \begin{figure}[ht]
%	% 	\centering
%	% 	\includegraphics[width=0.7\linewidth]{img/agline}
%	% 	\caption{stress-strain curve}
%	% 	\label{fig:ag_line}
%	% \end{figure}
%	
%	
%	\begin{figure}[ht]
%		\centering
%		\includegraphics[width=0.7\linewidth]{img/1stdiv}
%		\label{fig:surf}
%		\caption{stress-strain curve}
%	\end{figure}
%	
%	
%	\section{Conclusion}
%	%\bibliographystyle{elsarticle-num.bst}
%	
\reftitle{References}
\bibliography{ref/VIOLET-ref.bib}
\end{document}

>>>>

Defects such as grain boundary, void and segregation plays an significant role in the process of fracture \cite{Larsen2016}. In order to understanding the mechanism of brittle fracture, multi-scale methods from micro to marco scale have been applied to investigate the behavior of fracture. It's necessary to carefully examine the revolution of defects and its influence on the fracture process at atomic scale. A previous study on void growth in $\gamma$-TiAl single crystal has reveals that void with high volume fraction detracts incipient yield strength \cite{Tang2014}.Molecular dynamics(MD method has been use to investigate the evolution of void in materials in nanoscale \cite{Jing2018a,Elkhateeb2018,Tang2014}. The fracture mechanisms in the duplex micro-structure are plasticity induced grain boundary decohesion and cleavage, while those in the lamellar micro-structure are interface delamination and cracking across the lamellar \cite{Tang20}.

@@

The interaction of particle in the material is determined by interatomic potential. Many reported examples of crack propagation in metal materials were performed with embedded atomic method due to is better accuracy in metal lattice compare with F-S and L/J \cite{Ko2015}. The embedded atom method (MEAM) potential developed by Zope and Mishin \cite{Zope2003} was used in the study. The simulation is submitted by MD simulations with the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code \cite{Plimpton1995}. We performed constant-pressure and constant-temperature (NPT) molecular dynamics simulation. The definitnion of potential is as following:

@@

where $E_{total}$ is the total energy of the system, $\rho_{h,i}$, is the host electron density at atom $i$ due to the remaining atoms of the system,$F_i(\rho)$ is the energy for embedding atom $i$ into the background electron density $\rho$, and $\phi_{ij}(R_{ij})$ is the core-core pair repulsion between atoms $i$ and $j$ separated by the distance $R_{ij}$. It can be noted that $F_i$ only depends on the element of atom $i$ and $\phi_{ij}$ only depends on the elements of atoms $i$ and $j$. The electron density is, as stated above, approximated by the superposition of atomic densities.

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=1\linewidth]{img/models}
	\caption{Overview of model creation}
	\label{fig:model-creation}
\end{figure}

$\gamma $ TiAl has a fcc-centered tetragonal with an $L1_0$ structure, and $\alpha_2 -\rm TiAl$ is hcp structure, the structure of the two initial cells are shown in Fig.\ref{}, and the constructing parameters are givin by Table. \ref{tab:lattice_parameter}. The simulation cells of two phase polycrystalline with an initially spherical void at different position are shown in figure \cite{}. Periodic boundary conditions (PBC)are applied along all three directions, that makes poly crystal with periodic nanovoid structures. The initial dimension of simulation cell is  $L_x =20$ nm, $L_y = $18nm, $L_z = 21$ nm, and each model contains about 4.6 million atoms. The grain orientation and size were randomly created with Voronoi method with code ATOMSK \cite{}, and resulting in the arbitrary shape and orientation of the grains. Only one spherical void defect was placed intragranularlly or intergranularlly within each simulation model void within each simulation model. The intragranular spherical void was located in grain interior of the largest grain of the simulation model, as shown in Fig. \cite{}. The intergranular spherical void was at the center of the simulation cell, as shown in Fig. \cite{}.

@@

@@

\subsection{Deformation Behaviour of Two Phase Alloys without Void Defects}
However, the following discussion concentrates on deformation phenomena that rely on the elastoplastic codeformation of the $\gamma$ and $\alpha_2$ phases and on the particular point defect situation occurring in twophase alloys. Due to this effect ( $\alpha_2$ + $\gamma$ ) alloys exhibit some remarkable properties that are unlike those of either constituent.

\begin{figure}[ht]
		\centering
		\includegraphics[width=1\linewidth]{img/def-gamma}
		\label{fig:def-gamma}
		\caption{Defect evolution in $\gamma$ phase (perfect atoms of $\alpha$ phase have been removed)}
\end{figure}

The configure of atoms is shown in Fig.\ref{fig:yield}, it can be seen that dislication emission initiate in $\gamma$ pahse in XXX ps, and the deformation canbe mainly confied to the majority $\gamma$ pahse. $\gamma$(TiAl) deforms by octahedral glide of ordinary dislocations with the Burgers vector b=1/2<110] and superdislocations with the Burgers vectors $b=<101]$ and $b=1/2<11\overline{2}]$. The other potential deformation mode is mechanical twinning along $1/6<11\overline{2}]{111}$.

From Fig.\ref{fig:yield}, of the two constituents of ($\alpha_2$+$\gamma$) alloys, the $\alpha_2$ phase is more difficult to deform. A reason for the unequal strain partitioning between the $\alpha_2$ and $\gamma$ phase is certainly the strong plastic anisotropy of the $\alpha_2$ phase. TEM examinations performed on tensile  tested lamellar alloys have revealed that the limited plasticity of the $\alpha_2$ phase is mainly carried by local slip of <a>-type dislocations with the Burgers vector $b=1/3<11\overline{2}0>$ prism planes\ref{fig:yield}, which is by far the easiest slip system in $\alpha_2$ single crystals.

\begin{figure}[ht]
		\centering
		\includegraphics[width=1\linewidth]{img/def-alpha}
		\label{fig:def-alpha_2}
		\caption{Defect evolution in $\alpha_2$-phase (perfect atoms in $\alpha_2$ phase have been removed)}
	\end{figure}

@@

In many cases the orientation of slip slip is changed because the crystallographically available slip and directions are not continuous across the interface. This may significantly reduce the Schmid factor and thus impede slip transfer. At the $\gamma/\gamma$ interfaces the orientation of the slip plan could change through a relevantly large angle of about 90 degree. Reorientation of slip is always required at the $\alpha_{2}/\gamma$ interface; the smallest angle between the corresponding slip planes ${1 1 1}_{\gamma}$ and ${ 1 0 -1 0}_{\alpha_2}$ is about 19 degree \cite{}.

The core of  a dislocation intersecting an interface often needs to be transformed. For example, an ordinary 1/2<110] dislocation gliding in one $\gamma$ grain has to be converted in to a $<101]$ super dislocation with the double Burgers vector gliding in an adjacent $\gamma$ grain. At the $\alpha_2/\gamma$ interface the dislocations existing in the $D0_{19}$ structure have to be transformed into dislocations consistent with the $L1_0$structure. These core transformations are associated with a change of the dislocation line energy because the lengths of the Burgers vectors and the shear module are different.

@@

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=1\linewidth]{"img/dis-void2"}
	\caption{Orowan process in $\alpha$-phase ($\alpha$ phase atoms have been removed)}
	\label{fig:dis-void}
\end{figure}

@@

@@

According to Schmid's law:
	$$\tau = \sigma*m$$
where m is the Schmid factor :
	$$ m = cos(\phi)cos(\lambda)$$

\reftitle{References}
\bibliography{ref/VIOLET-ref.bib}
\end{document}
